---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
```

```{r}
tweet <- read_csv("data/code_clan_tweets.csv")
```

```{r}

head(tweet)
dim(tweet)
names(tweet)
```



#Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
favtweet <- tweet %>% 
  select(favorite_count, is_quote) %>% 
  filter(is_quote != TRUE) %>% 
  summarise(total_count = sum(favorite_count))

head(favtweet)
```


```{r}
names(tweet)
```


#Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
tweet %>% 
  filter(is_quote != TRUE) %>% 
  group_by(source) %>% 
  
  summarise(retweet_mean = mean(retweet_count)) %>% 

arrange(desc(retweet_mean))

```
#Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.



```{r}
names(tweet)


```


#Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.


```{r}
tweet_selected <- select(tweet, tweet_id, favorite_count, media_type) 
tweet_selected
```



```{r}
tweet_selected %>% 
  summarise(na_text = sum(is.na(media_type)))
```

```{r}
imputed_tweet <- tweet_selected %>% 
  mutate(media_type = coalesce(media_type, "text"))

imputed_tweet

```




```{r}

```


```{r}
imputed_tweet %>% 
 
  group_by(media_type) %>% 
  
  summarise(fav_count= sum(favorite_count)) %>% 

  arrange(desc(fav_count))
```


#Find the mean number of characters that a CodeClan tweet contains.



```{r}




```

#The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.



```{r}

```

#From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.

```{r}

```

