---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(janitor)
```



# MVP

## Joins

<br>
**Question 1**

Read in all 4 credit card transaction datasets and clean column names.

```{r}


cust <- read_csv("data/CustomerBase.csv")

card <- read_csv("data/CardBase.csv")

fraud <- read_csv("data/FraudBase.csv")

transact <- read_csv("data/TransactionBase.csv")

clean_names(cust)

clean_names(card)

clean_names(fraud)

clean_names(transact)

```




**Question 2**

Join the data containing card details and customer details by customer id, so that all records of card details and any matching records in customer details are kept. Before you run the code, think about how many rows you expect to see after joining.

```{r}
# Thinking there should be 500 records as there are 500 card records
card_cust <- inner_join(card, cust, "Cust_ID")

card_cust

```






**Question 3**

Join the data containing fraud details with transaction details so all rows of both tables are kept. What does the resulting row number tell you?


```{r}
fraud_trans <- full_join(fraud, transact, by = "Transaction_ID") %>% view

fraud_trans
```





**Question 4**

Join the data containing card details with transaction details so rows from the first which have matching ones in the second are returned, but only return rows in the first table once.



```{r}

# Not sure how to do the last bit to this (i.e what the question is asking ??  Show one transaction per card??)

card_trans  <- left_join(card_cust, transact, by = c("Card_Number" = "Credit_Card_ID"))


card_trans
```
```{r}

  grouped_card <- group_by(card_trans, Card_Number)
  summarise(grouped_card, count =n())
```


## `tidyr`

**Question 5**

Read in `hat_observations` and separate `observation` into two columns, `hat_colour` and `hat_type`.
```{r}
hat <- read_csv("data/hat_observations.csv")


```

```{r}
#separate `observation` into two columns, `hat_colour` and `hat_type
observ_split <-
hat %>% 
separate(
  col = observation,
  into = c("hat_colour" , "hat_type"),
  sep = ","
) 
observ_split
```




**Question 6**

Unite `day`, `month`, and `year` columns into a column called `date` using a suitable separator. Then find the date where the most berets were observed.


```{r}

observ_split %>% 
  unite(
    col = "Date",
    c(day, month, year),
    sep = "/"
  ) %>% 
filter(hat_type == "beret") %>% 
arrange(desc(observation_count))


```

# Extension

## Joins

**Question 1**

Can you join all 4 datasets together so that you're left with a dataset that looks like below with **109 rows** and **12 columns**?


```{r}
# Join cardTrans and fraud together

all_card_data <- inner_join(card_trans,fraud,by ="Transaction_ID")


all_card_data
```
**Question 2**

Read in exam_scores and transform it into long format with two new columns exam_question and score. Then, using separate and select, remove superfluous information from the values in exam_question
```{r}


exam <- read_csv("data/exam_scores.csv")

```

```{r}
head(exam)

```

```{r}
exam_split <-
exam %>% 
  pivot_longer(
    cols = c(exam_Q1:exam_Q10),
    names_to = "exam_question",
    values_to = "exam_score",
    ) %>% 
  separate(
  col = exam_question,
  into = c("text" , "question"),
  sep = "_"
) %>% 
  select(id, question, exam_score)
exam_split

```

