---
title: "`dplyr` Weekend Homework"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```
<br>



As this is your first weekend homework, here are some tips: 

* Try to schedule some time in your weekend to work on the homework so it's not suddenly Monday morning and you haven't gotten started yet (it happens).
* Remember that the weekend homework is for your learning, so try to use it as an opportunity to apply and consolidate everything you've learned in the week.
* Also use it as an opportunity to spend a bit more time making your code readable and reproducible, by practising commenting and writing some text around your steps and findings. You will thank yourself later! 
  * This will be especially useful for this specific weekend homework as it's very open-ended and you will eventually forget your own thought process
* A bit obvious, but don't spend your entire weekend working on the homework! Remember to spend time doing things you enjoy and rest up ahead of the following week.

The data for this weekend homework is scraped from Goodreads (a website all about books) and made publicly available on Kaggle. You can read more about the data [here](https://www.kaggle.com/jealousleopard/goodreadsbooks).

# MVP

### First steps

Load necessary packages and read in `books.csv`. Investigate dimensions, variables, missing values - you know the drill!

### Up to you

Now it's up to you... For this weekend homework there will be no specific tasks, just you and this dataset! Using everything you've learned this week, try to describe/summarise at least 5 things about this dataset - using R and the tidyverse of course! Feel free to find and use new functions if there is something that the tidyverse doesn't offer, but do try to use this homework to apply what you have learned this week. Be prepared to share one of your findings on Monday!

### Remember

Before you submit, go through your weekend homework and make sure your code is following best practices as laid out in the `coding_best_practice` lesson.



```{r}
library(tidyverse)
library(dplyr)
```



```{r}
books <- read_csv("data/books.csv")
```
```{r}
#view high level data to understand what I have got
head(books)
```

```{r}
# Check overall dimensions of data set and variable names
dim(books)
names(books)
```


```{r}

#create new tab to view books data in tabular form 
view(books)

# print the data in console to view 
books

# want to see the data types I have in data set
glimpse(books)
        
```

#   INITIAL THOUGHTS ARE:
#   what data types?
#   are there any data missing?
#   are the data in right format?
#   any data missing?
#   What is isbn and isbn13 data telling me?

#   Rating is based on differing survey population counts

#   Some books have multiple authors
#   we have a mixture of character fields <chr> and decimal numbers <dbl>
#   average rating could be used to give top 5 and bottom 5 books
#   might want to know book counts by author or publisher
#   might want to know how many book published by year
#   might want to know how many books by each publisher 


```{r}
books %>%
summarise(across(.fns = ~sum(is.na(.x))))
```
#   average rating missing in three rows - could insert median 

```{r}

  missing_author <- filter(books,is.na(authors))
   

missing_author

```
#   Row 40146 hasnt loaded in properly and has multiple data columns within title column, need to fix source file #   to split dat properly


```{r}

missing_rating <- filter(books, is.na(average_rating))
    
missing_rating
```
```{r}
missing_pages <- filter(books, is.na(num_pages))
    
missing_pages
```

```{r}
missing_pages <- filter(books, is.na(num_pages))

missing_rating <- filter(books, is.na(average_rating))
    
missing_author <- filter(books,is.na(authors))
   

missing_author    
    
missing_rating    
missing_pages
```
















































